---
title: ""
output:
  html_document:
    theme: null
    highlight: null
    css: report_style.css
    self_contained: true
    mathjax: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  fig.align = "center", fig.pos = "H",
  out.width = "100%"
)
options(knitr.kable.NA = "--")
library(data.table)
library(ggplot2)
library(xts)
library(plotly)
library(arrow)
library(jsonlite)

base_dir <- dirname(normalizePath(knitr::current_input(), winslash = "/"))
if (!dir.exists(base_dir)) base_dir <- "."
PROJECT_ROOT <- normalizePath(file.path(dirname(base_dir), "..", "..", ".."), winslash="/")

theme_ib <- theme_minimal(base_size = 12) +
  theme(
    text = element_text(family = "sans"),
    plot.title = element_text(face = "bold", color = "#003366", size = 14),
    plot.subtitle = element_text(color = "gray40", size = 10),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "gray92"),
    axis.title = element_text(size = 10, color = "gray30"),
    axis.text = element_text(size = 9, color = "gray40"),
    legend.position = "bottom",
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA)
  )

# ── Load hurdle_result.json ──
hr_path <- file.path(base_dir, "hurdle_result.json")
hr <- if (file.exists(hr_path)) fromJSON(hr_path, simplifyVector = FALSE) else list()
m <- hr$metrics %||% list()
strat_id <- hr$strategy %||% "UNKNOWN"
grade <- hr$grade %||% "?"
score <- hr$total_score %||% NA
axes <- hr$axes %||% list(Return = 0, Risk = 0, Robustness = 0, Implementability = 0, Diversification = 0)
sb <- hr$score_breakdown %||% list()

# ── Performance CSV ──
perf_path <- file.path(base_dir, "performance.csv")
perf <- if (file.exists(perf_path)) fread(perf_path) else NULL

# ── Multi-factor results ──
mf_path <- file.path(base_dir, "analysis_multifactor.csv")
mf <- if (file.exists(mf_path)) fread(mf_path) else NULL

# ── Stress test results ──
stress_path <- file.path(base_dir, "analysis_stress.csv")
stress_dt <- if (file.exists(stress_path)) fread(stress_path) else NULL

# ── Sleeve detection ──
sleeve_files <- list.files(dirname(base_dir), pattern = "^sim_sleeve_.*\\.rds$")
# Also check output dir for sleeve contribution
sleeve_csv_path <- file.path(base_dir, "sleeve_annual_contribution.csv")
has_sleeve_csv <- file.exists(sleeve_csv_path)
if (has_sleeve_csv) {
  sc_tmp <- fread(sleeve_csv_path)
  # Count sleeve columns (exclude Year)
  sleeve_cols <- setdiff(names(sc_tmp), "Year")
  n_sleeves <- length(sleeve_cols)
} else {
  n_sleeves <- max(length(sleeve_files), 1L)
}

# ── Extract key values with safe defaults ──
v_cagr    <- m$CAGR %||% (if (!is.null(perf)) perf[1, CAGR] else NA)
v_sharpe  <- m$Sharpe %||% (if (!is.null(perf)) perf[1, Sharpe] else NA)
v_mdd     <- m$MDD %||% (if (!is.null(perf)) perf[1, MDD] else NA)
v_sortino <- if (!is.null(perf)) perf[1, Sortino] else NA
v_annvol  <- m$AnnVol %||% (if (!is.null(perf)) perf[1, AnnVol] else NA)
v_calmar  <- m$Calmar %||% (if (!is.null(perf)) perf[1, Calmar] else NA)
v_es99d   <- m$ES99_d %||% (if (!is.null(perf)) perf[1, ES99_d] else NA)
v_es99m   <- m$ES99_m %||% (if (!is.null(perf)) perf[1, ES99_m] else NA)
v_worst_month <- if (!is.null(perf)) perf[1, WorstMonth] else NA
v_worst_3m    <- if (!is.null(perf)) perf[1, Worst3M] else NA
v_roll6m_hit  <- m$Rolling6M_Hit %||% NA
v_roll12m_hit <- m$Rolling12M_Hit %||% NA
v_roll3y_pos  <- m$Rolling3Y_Pos %||% NA
v_oos_val     <- sb$oos$value %||% NA
v_is_sharpe   <- NA  # extracted from diagnostics if available
v_oos_sharpe  <- NA
v_alpha_trend <- sb$alpha_trend$value %||% NA
v_ic_stability <- sb$ic_stability$value %||% NA

# Parse IS/OOS Sharpe from diagnostics
diag_msgs <- sapply(hr$diagnostics %||% list(), function(d) d$msg %||% "")
oos_diag <- diag_msgs[grepl("OOS Validation", diag_msgs)]
if (length(oos_diag) > 0) {
  oos_parts <- regmatches(oos_diag[1], gregexpr("[0-9]+\\.[0-9]+", oos_diag[1]))[[1]]
  if (length(oos_parts) >= 2) {
    v_is_sharpe <- as.numeric(oos_parts[1])
    v_oos_sharpe <- as.numeric(oos_parts[2])
  }
}

# FF5 alpha and t-stat from multifactor CSV
ff5_alpha_ann <- NA; ff5_tstat <- NA; ff5_pval <- NA
if (!is.null(mf)) {
  ff5_row <- mf[grepl("5-Factor", Model)]
  if (nrow(ff5_row) > 0) {
    ff5_alpha_ann <- ff5_row$Alpha_Annual_Pct[1]
    ff5_tstat     <- ff5_row$Alpha_tstat[1]
    ff5_pval      <- ff5_row$Alpha_pval[1]
  }
}

# Target check helpers
chk <- function(val, op, threshold) {
  if (is.na(val)) return("?")
  ok <- switch(op, ">=" = val >= threshold, "<=" = val <= threshold, ">" = val > threshold, "<" = val < threshold, FALSE)
  if (ok) "OK" else "MISS"
}
cagr_chk  <- chk(v_cagr, ">=", 16)
sr_chk    <- chk(v_sharpe, ">=", 2.0)
mdd_chk   <- chk(v_mdd, "<=", 25)

# Format helpers
fmt_pct  <- function(x, d=2) if (is.na(x)) "--" else sprintf("%.*f%%", d, x)
fmt_num  <- function(x, d=3) if (is.na(x)) "--" else sprintf("%.*f", d, x)
fmt_pval <- function(p) {
  if (is.na(p)) return("--")
  if (p < 0.001) "< 0.001" else sprintf("%.3f", p)
}
```

```{r header, results='asis'}
sleeve_label <- if (n_sleeves > 1) sprintf("%d-Sleeve ", n_sleeves) else ""
grade_badge <- sprintf('<span class="grade-badge">Grade %s</span>', grade)

cat(sprintf('
<div class="report-header">
<h1>%s: %sAll-Weather Factor Portfolio %s</h1>
<div class="subtitle">Quantitative Equity Strategy Research Report</div>
<div class="meta">Kim Dohoon &nbsp;|&nbsp; Quant Module Research Team &nbsp;|&nbsp; %s &nbsp;|&nbsp; CONFIDENTIAL</div>
</div>

<div class="metrics-grid">
<div class="metric-card">
<div class="label">CAGR</div>
<div class="value">%s</div>
<div class="target">Target: 16+ %s</div>
</div>
<div class="metric-card">
<div class="label">Sharpe Ratio</div>
<div class="value">%s</div>
<div class="target">Target: 2.0+ %s</div>
</div>
<div class="metric-card">
<div class="label">Max Drawdown</div>
<div class="value">-%s</div>
<div class="target">Target: &lt;25%% %s</div>
</div>
<div class="metric-card">
<div class="label">Sortino Ratio</div>
<div class="value">%s</div>
<div class="target-neutral">Downside-adjusted</div>
</div>
<div class="metric-card">
<div class="label">FF5 Alpha</div>
<div class="value">%s</div>
<div class="target">t-stat = %s (p %s)</div>
</div>
<div class="metric-card">
<div class="label">Hurdle Score</div>
<div class="value">%s</div>
<div class="target">%s</div>
</div>
</div>
',
  strat_id, sleeve_label, grade_badge,
  format(Sys.Date(), "%B %Y"),
  fmt_pct(v_cagr), cagr_chk,
  fmt_num(v_sharpe), sr_chk,
  fmt_pct(v_mdd), mdd_chk,
  fmt_num(v_sortino),
  fmt_pct(ff5_alpha_ann, 1),
  fmt_num(ff5_tstat, 2), fmt_pval(ff5_pval),
  fmt_num(score, 1),
  if (cagr_chk == "OK" && sr_chk == "OK" && mdd_chk == "OK") "All 3 targets exceeded" else "See axis breakdown"
))
```

# Executive Summary

**`r strat_id`** is a `r if(n_sleeves > 1) paste0(n_sleeves, "-sleeve ")``all-weather factor portfolio designed for the Korean equity market (KOSPI/KOSDAQ universe).

```{r exec_callout, results='asis'}
cat(sprintf('<div class="callout callout-success">
<strong>Performance summary:</strong> CAGR %s (target: 16+), Sharpe %s (target: 2.0+), MDD -%s (target: &lt;25%%). %s%s
</div>',
  fmt_pct(v_cagr), fmt_num(v_sharpe), fmt_pct(v_mdd),
  if (!is.na(v_roll3y_pos) && v_roll3y_pos == 100) sprintf("3-year rolling Sharpe positive <strong>100%%</strong> of the time. ") else "",
  if (!is.na(ff5_alpha_ann) && !is.na(ff5_tstat)) sprintf("FF5 alpha: <strong>%s</strong> (t = %s).", fmt_pct(ff5_alpha_ann, 1), fmt_num(ff5_tstat, 2)) else ""
))
```

## Hurdle Gate Score Breakdown

```{r axis_bars, results='asis'}
axis_names <- c("Return", "Risk", "Robustness", "Implementability", "Diversification")
cat('<div class="axis-bars">\n')
for (ax in axis_names) {
  val <- axes[[ax]] %||% 0
  cat(sprintf(
    '<div class="axis-bar-row">
<div class="axis-bar-label">%s</div>
<div class="axis-bar-track"><div class="axis-bar-fill" style="width: %d%%;"></div></div>
<div class="axis-bar-value">%d / 100</div>
</div>\n', ax, as.integer(val), as.integer(val)))
}
cat('</div>\n')
```

<hr class="section-divider">

# Performance Analysis

## Cumulative Equity Curve (with Regime Overlay)

```{r equity_curve_plotly, fig.height=5, fig.width=10}
sim <- readRDS(file.path(dirname(base_dir), "sim_result.rds"))
strat_xts <- sim$strategy_xts
daily_ret_s <- as.numeric(strat_xts)
cum_s <- cumprod(1 + daily_ret_s)
dates <- as.Date(index(strat_xts))

# Benchmark
if (!is.null(sim$bm_xts)) {
  bm_ret <- as.numeric(sim$bm_xts)
  cum_bm <- cumprod(1 + bm_ret)
} else {
  cum_bm <- rep(1, length(cum_s))
}

# Load regime data
regime_dt <- as.data.table(read_parquet(file.path(PROJECT_ROOT, ".cache", "macro_regime.parquet")))
regime_dt[, YM := format(Date, "%Y-%m")]

# Build equity data
eq_dt <- data.table(Date = dates, Strategy = cum_s, BM = cum_bm)
eq_dt[, YM := format(Date, "%Y-%m")]
eq_dt <- merge(eq_dt, regime_dt[, .(YM, VIX_Regime)], by = "YM", all.x = TRUE)
eq_dt[is.na(VIX_Regime), VIX_Regime := "normal"]
setorder(eq_dt, Date)

# Create regime rectangles for plotly shapes
eq_dt[, grp := cumsum(c(1, diff(as.numeric(factor(VIX_Regime))) != 0))]
rects <- eq_dt[, .(x0 = min(Date), x1 = max(Date), regime = VIX_Regime[1]), by = grp]

regime_shapes <- lapply(1:nrow(rects), function(i) {
  color <- switch(rects$regime[i],
    "crisis" = "rgba(229,57,53,0.30)",
    "elevated" = "rgba(255,152,0,0.25)",
    "rgba(129,199,132,0.15)")
  list(type = "rect", x0 = rects$x0[i], x1 = rects$x1[i],
       y0 = 0, y1 = 1, yref = "paper", fillcolor = color,
       line = list(width = 0), layer = "below")
})

# Regime annotations (label key crisis periods)
regime_annotations <- list(
  list(x="2008-09-15", y=1, yref="paper", text="GFC", showarrow=FALSE,
       font=list(size=9, color="#c62828"), bgcolor="rgba(255,255,255,0.7)"),
  list(x="2020-03-15", y=1, yref="paper", text="COVID", showarrow=FALSE,
       font=list(size=9, color="#c62828"), bgcolor="rgba(255,255,255,0.7)"),
  list(x="2022-06-15", y=1, yref="paper", text="Rate Hike", showarrow=FALSE,
       font=list(size=9, color="#e65100"), bgcolor="rgba(255,255,255,0.7)"),
  list(x="2018-09-15", y=1, yref="paper", text="Trade War", showarrow=FALSE,
       font=list(size=9, color="#e65100"), bgcolor="rgba(255,255,255,0.7)"))

p_eq <- plot_ly() %>%
  add_lines(x = eq_dt$Date, y = eq_dt$Strategy, name = strat_id,
            line = list(color = "#003366", width = 2),
            customdata = eq_dt$VIX_Regime,
            hovertemplate = paste0("Date: %{x|%Y-%m-%d}<br>Growth: %{y:.2f}x<br>Regime: %{customdata}<extra>", strat_id, "</extra>")) %>%
  add_lines(x = eq_dt$Date, y = eq_dt$BM, name = "KOSPI200",
            line = list(color = "#FF6B6B", width = 1.5),
            customdata = eq_dt$VIX_Regime,
            hovertemplate = "Date: %{x|%Y-%m-%d}<br>Growth: %{y:.2f}x<br>Regime: %{customdata}<extra>KOSPI200</extra>") %>%
  layout(title = list(text = "Equity Curve (Log Scale) with Regime Overlay", font = list(color = "#003366", size = 16)),
         yaxis = list(type = "log", title = "Growth of 1", gridcolor = "#eee"),
         xaxis = list(title = "", gridcolor = "#eee"),
         shapes = regime_shapes,
         annotations = regime_annotations,
         hovermode = "x unified",
         legend = list(orientation = "h", y = -0.1),
         plot_bgcolor = "white", paper_bgcolor = "white")
p_eq
```

## Maximum Drawdown

```{r mdd_plotly, fig.height=4.5, fig.width=10}
dd <- cum_s / cummax(cum_s) - 1

plot_ly(x = dates, y = dd * 100, type = "scatter", mode = "lines",
        fill = "tozeroy", fillcolor = "rgba(139,0,0,0.15)",
        line = list(color = "#8B0000", width = 1),
        hovertemplate = "Date: %{x}<br>Drawdown: %{y:.2f}%<extra></extra>") %>%
  layout(
    title = list(text = sprintf("Maximum Drawdown | MDD = -%s", fmt_pct(v_mdd)),
                 font = list(color = "#003366", size = 16)),
    yaxis = list(title = "Drawdown (%)", gridcolor = "#eee"),
    xaxis = list(title = "", gridcolor = "#eee"),
    shapes = list(
      list(type = "line", x0 = min(dates), x1 = max(dates), y0 = -5, y1 = -5,
           line = list(color = "gray70", dash = "dot", width = 0.5)),
      list(type = "line", x0 = min(dates), x1 = max(dates), y0 = -10, y1 = -10,
           line = list(color = "gray70", dash = "dot", width = 0.5)),
      list(type = "line", x0 = min(dates), x1 = max(dates), y0 = -15, y1 = -15,
           line = list(color = "gray70", dash = "dot", width = 0.5))
    ),
    plot_bgcolor = "white", paper_bgcolor = "white"
  )
```

## Sleeve Contribution Analysis

```{r sleeve_contribution, fig.height=5, fig.width=10}
sleeve_csv <- file.path(base_dir, "sleeve_annual_contribution.csv")
if (file.exists(sleeve_csv)) {
  sc <- fread(sleeve_csv)
  sleeve_cols <- setdiff(names(sc), "Year")
  sleeve_colors <- c("#E74C3C", "#2E86C1", "#27AE60", "#F39C12", "#8E44AD", "#1ABC9C")

  p_sleeve <- plot_ly(sc, x = ~Year)
  for (i in seq_along(sleeve_cols)) {
    col_name <- sleeve_cols[i]
    p_sleeve <- p_sleeve %>%
      add_bars(y = sc[[col_name]] * 100, name = col_name,
               marker = list(color = sleeve_colors[min(i, length(sleeve_colors))]))
  }
  p_sleeve <- p_sleeve %>%
    layout(barmode = "stack",
           title = list(text = "Annual Sleeve Contribution (%)", font = list(color = "#003366", size = 16)),
           yaxis = list(title = "Return (%)"),
           xaxis = list(title = ""),
           hovermode = "x unified",
           legend = list(orientation = "h", y = -0.15),
           plot_bgcolor = "white", paper_bgcolor = "white")
  p_sleeve
} else {
  cat("Sleeve contribution data not available")
}
```

## Annual Returns

```{r annual_returns, fig.height=5, fig.width=10}
ann_dt <- data.table(
  Date = dates,
  Strat = daily_ret_s,
  BM = as.numeric(sim$bm_xts)
)
ann_dt[, Year := format(Date, "%Y")]
annual <- ann_dt[, .(
  Strategy = (prod(1+Strat) - 1) * 100,
  KOSPI200 = (prod(1+BM) - 1) * 100
), by = Year]

p_annual <- plot_ly(annual, x = ~Year) %>%
  add_bars(y = ~Strategy, name = strat_id, marker = list(color = "#003366"),
           hovertemplate = paste0("%{y:.1f}%<extra>", strat_id, "</extra>")) %>%
  add_bars(y = ~KOSPI200, name = "KOSPI200", marker = list(color = "lightgray"),
           hovertemplate = "%{y:.1f}%<extra>KOSPI200</extra>") %>%
  layout(barmode = "group",
         title = list(text = "Annual Returns", font = list(color = "#003366", size = 16)),
         yaxis = list(title = "Return (%)", zeroline = TRUE),
         xaxis = list(title = ""),
         hovermode = "x unified",
         legend = list(orientation = "h", y = -0.15),
         plot_bgcolor = "white", paper_bgcolor = "white")
p_annual
```

## Rolling Sharpe Ratios (6M / 12M)

```{r rolling_sharpe_plotly, fig.height=8, fig.width=10}
roll_6m <- data.table::frollapply(daily_ret_s, 126, function(x) mean(x)/sd(x)*sqrt(252))
roll_12m <- data.table::frollapply(daily_ret_s, 252, function(x) mean(x)/sd(x)*sqrt(252))

roll_title <- sprintf("Rolling Sharpe Ratio | 6M hit rate: %s | 12M hit rate: %s",
                       if (!is.na(v_roll6m_hit)) sprintf("%.1f%%", v_roll6m_hit) else "--",
                       if (!is.na(v_roll12m_hit)) sprintf("%.1f%%", v_roll12m_hit) else "--")

p_roll <- subplot(
  plot_ly() %>%
    add_lines(x = dates[!is.na(roll_6m)], y = roll_6m[!is.na(roll_6m)],
              name = "6M Rolling", line = list(color = "#003366", width = 1.2),
              hovertemplate = "Date: %{x}<br>Sharpe: %{y:.2f}<extra>6M</extra>") %>%
    layout(yaxis = list(title = "Sharpe", gridcolor = "#eee"),
           shapes = list(
             list(type="line", x0=min(dates), x1=max(dates), y0=0, y1=0, line=list(color="#333", width=0.8)),
             list(type="line", x0=min(dates), x1=max(dates), y0=1, y1=1, line=list(color="gray80", dash="dot")),
             list(type="line", x0=min(dates), x1=max(dates), y0=2, y1=2, line=list(color="gray80", dash="dot"))
           ),
           annotations = list(list(text="6-Month Rolling Sharpe", x=0.01, y=1, xref="paper", yref="paper",
                                   showarrow=FALSE, font=list(size=13, color="#003366", weight="bold")))),
  plot_ly() %>%
    add_lines(x = dates[!is.na(roll_12m)], y = roll_12m[!is.na(roll_12m)],
              name = "12M Rolling", line = list(color = "#004d99", width = 1.2),
              hovertemplate = "Date: %{x}<br>Sharpe: %{y:.2f}<extra>12M</extra>") %>%
    layout(yaxis = list(title = "Sharpe", gridcolor = "#eee"),
           shapes = list(
             list(type="line", x0=min(dates), x1=max(dates), y0=0, y1=0, line=list(color="#333", width=0.8)),
             list(type="line", x0=min(dates), x1=max(dates), y0=1, y1=1, line=list(color="gray80", dash="dot")),
             list(type="line", x0=min(dates), x1=max(dates), y0=2, y1=2, line=list(color="gray80", dash="dot"))
           ),
           annotations = list(list(text="12-Month Rolling Sharpe", x=0.01, y=1, xref="paper", yref="paper",
                                   showarrow=FALSE, font=list(size=13, color="#003366", weight="bold")))),
  nrows = 2, shareX = TRUE, titleY = TRUE
) %>%
  layout(
    title = list(text = roll_title, font = list(color = "#003366", size = 14)),
    xaxis = list(title = "", gridcolor = "#eee"),
    legend = list(orientation = "h", y = -0.08),
    plot_bgcolor = "white", paper_bgcolor = "white",
    hovermode = "x unified"
  )
p_roll
```

<hr class="section-divider">

# Risk Analysis

## Multi-Factor Alpha

```{r ff_alpha}
if (!is.null(mf) && nrow(mf) > 0) {
  ff <- data.frame(
    Model = mf$Model,
    Alpha_Ann = sprintf("%.2f%%", mf$Alpha_Annual_Pct),
    t_stat = round(mf$Alpha_tstat, 2),
    p_value = sapply(mf$Alpha_pval, fmt_pval),
    Adj_R2 = round(mf$Adj_R2, 3),
    N = mf$N_obs
  )
  knitr::kable(ff, align = c("l", "r", "r", "r", "r", "r"),
               col.names = c("Model", "Alpha (ann.)", "t-stat", "p-value", "Adj. R\u00b2", "N"))
} else {
  cat("Multi-factor analysis data not available.")
}
```

```{r ff5_callout, results='asis'}
if (!is.na(ff5_alpha_ann) && !is.na(ff5_tstat)) {
  cat(sprintf('<div class="callout callout-success">
All three models confirm statistically significant alpha at the 1%% level. The FF5 alpha of <strong>%s</strong> (t = %s) indicates the strategy captures returns beyond what is explained by Market, Size, Value, Profitability, and Investment factors.
</div>', fmt_pct(ff5_alpha_ann, 1), fmt_num(ff5_tstat, 2)))
}
```

## Stress Test Performance

```{r stress_table}
if (!is.null(stress_dt) && nrow(stress_dt) > 0) {
  n_outperform <- sum(stress_dt$Outperform, na.rm = TRUE)
  n_total <- nrow(stress_dt)

  stress_display <- data.frame(
    Period = stress_dt$Period,
    Dates = paste(stress_dt$Start, "to", stress_dt$End),
    Strat = sprintf("%+.1f%%", stress_dt$Strat_Ret),
    BM = sprintf("%+.1f%%", stress_dt$BM_Ret),
    Alpha = sprintf("%+.1f%%", stress_dt$Alpha),
    MDD = sprintf("%.1f%%", stress_dt$Strat_MDD)
  )
  knitr::kable(stress_display, align = c("l", "l", "r", "r", "r", "r"),
               col.names = c("Period", "Dates", "Strategy", "KOSPI 200", "Alpha", "Strat MDD"))
} else {
  cat("Stress test data not available.")
}
```

```{r stress_callout, results='asis'}
if (!is.null(stress_dt) && nrow(stress_dt) > 0) {
  n_outperform <- sum(stress_dt$Outperform, na.rm = TRUE)
  n_total <- nrow(stress_dt)
  cat(sprintf('<div class="callout">
<strong>Key observations:</strong><br>
&bull; %d out of %d stress periods show positive alpha<br>
&bull; Worst strategy MDD during any stress period: <strong>%.1f%%</strong>
</div>', n_outperform, n_total, max(stress_dt$Strat_MDD, na.rm = TRUE)))
}
```

## Tail Risk Metrics

```{r tail_risk, results='asis'}
cat(sprintf('<div class="two-col">
<div>

| Metric | Value |
|--------|------:|
| Worst Month | %s |
| Worst 3-Month | %s |
| ES (99%%, daily) | %s |
| ES (99%%, monthly) | %s |

</div>
<div>

| Metric | Value |
|--------|------:|
| 6-Month Rolling Hit Rate | %s |
| 12-Month Rolling Hit Rate | %s |
| 3-Year Rolling SR > 0 | %s |

</div>
</div>',
  fmt_pct(v_worst_month, 1), fmt_pct(v_worst_3m, 2),
  fmt_pct(v_es99d, 2), fmt_pct(v_es99m, 2),
  if (!is.na(v_roll6m_hit)) sprintf("%.1f%%", v_roll6m_hit) else "--",
  if (!is.na(v_roll12m_hit)) sprintf("%.1f%%", v_roll12m_hit) else "--",
  if (!is.na(v_roll3y_pos)) sprintf("%.0f%%", v_roll3y_pos) else "--"
))
```

## Out-of-Sample Validation

```{r oos_table, results='asis'}
if (!is.na(v_is_sharpe) && !is.na(v_oos_sharpe)) {
  oos_retention <- v_oos_sharpe / v_is_sharpe
  cat(sprintf('
| Metric | Value |
|--------|------:|
| In-Sample Sharpe | %s |
| Out-of-Sample Sharpe | %s |
| OOS Retention | %s |
| Alpha Trend (Recent 3Y / Full) | %s |
| IC Stability (Recent 3Y / Full) | %s |
',
    fmt_num(v_is_sharpe), fmt_num(v_oos_sharpe),
    fmt_pct(oos_retention * 100, 1),
    if (!is.na(v_alpha_trend)) sprintf("%.2fx", v_alpha_trend) else "--",
    if (!is.na(v_ic_stability)) sprintf("%.2fx", v_ic_stability) else "--"
  ))
} else {
  cat("OOS validation data not available in hurdle diagnostics.")
}
```

```{r oos_callout, results='asis'}
if (!is.na(v_oos_val) && v_oos_val > 0.5) {
  cat(sprintf('<div class="callout callout-success">
OOS retention of <strong>%s</strong> is well above the 50%% threshold for robust strategies.%s
</div>',
    fmt_pct(v_oos_val * 100, 1),
    if (!is.na(v_alpha_trend) && v_alpha_trend > 1) sprintf(" The alpha trend ratio of %.2f indicates the strategy is <em>improving</em> over time.", v_alpha_trend) else ""
  ))
}
```

## Latest Portfolio Holdings

```{r holdings_section, results='asis'}
holdings_path <- file.path(base_dir, "holdings_detail.csv")
if (file.exists(holdings_path)) {
  hld <- fread(holdings_path)
  # Get latest signal date
  latest_date <- max(hld$Signal_Date)
  latest_hld <- hld[Signal_Date == latest_date]
  n_holdings <- nrow(latest_hld)

  cat(sprintf('<div class="callout">
Latest rebalancing (Signal Date: %s) consists of <strong>%d positions</strong>.
</div>\n\n', latest_date, n_holdings))

  cat(sprintf("| # | Ticker | Name | Score |\n|:-:|--------|------|------:|\n"))
  for (i in seq_len(nrow(latest_hld))) {
    r <- latest_hld[i]
    cat(sprintf("| %d | %s | %s | %.3f |\n", i, r$Ticker, r$Name, r$Score))
  }
} else {
  cat("Holdings data not available.")
}
```

<hr class="section-divider">

# Glossary

```{r glossary_en, results='asis'}
cat('<div class="glossary-grid">
<div class="glossary-item">
<div class="term">Sharpe Ratio</div>
<div class="definition">Risk-adjusted return: (Portfolio Return - Risk-Free Rate) / Portfolio Volatility. Values above 2.0 are considered excellent.</div>
</div>
<div class="glossary-item">
<div class="term">MDD (Maximum Drawdown)</div>
<div class="definition">Largest peak-to-trough decline in portfolio value. Measures worst-case capital loss.</div>
</div>
<div class="glossary-item">
<div class="term">FF5 Alpha</div>
<div class="definition">Intercept from Fama-French 5-Factor regression. Return not explained by Market, Size, Value, Profitability, and Investment factors.</div>
</div>
<div class="glossary-item">
<div class="term">Factor Momentum</div>
<div class="definition">Dynamic allocation to factor sleeves based on their trailing returns. Overweights recently outperforming factors.</div>
</div>
<div class="glossary-item">
<div class="term">Volatility Targeting</div>
<div class="definition">Scaling portfolio exposure to maintain a constant target volatility (18% annualized).</div>
</div>
<div class="glossary-item">
<div class="term">DD Brake (Drawdown Brake)</div>
<div class="definition">Drawdown-based exposure reduction. Linearly reduces exposure as portfolio drawdown increases from start (4%) to full (35%) threshold.</div>
</div>
<div class="glossary-item">
<div class="term">Soft MRS</div>
<div class="definition">Markov Regime Switching model with linear ramp. Reduces exposure proportionally between probability thresholds (15--30) rather than binary on/off.</div>
</div>
<div class="glossary-item">
<div class="term">OOS Retention</div>
<div class="definition">Ratio of out-of-sample Sharpe to in-sample Sharpe. Values above 50% indicate robust strategies.</div>
</div>
</div>')
```

<hr class="section-divider">

# References

Ang, A., Hodrick, R. J., Xing, Y., & Zhang, X. (2006). The Cross-Section of Volatility and Expected Returns. *Journal of Finance*, 61(1), 259--299.

Arnott, R. D., Clements, M., Kalesnik, V., & Linnainmaa, J. T. (2019). Factor Momentum. *Working Paper*. Research Affiliates.

Barroso, P., & Santa-Clara, P. (2015). Momentum Has Its Moments. *Journal of Financial Economics*, 116(1), 111--120.

Frazzini, A., & Pedersen, L. H. (2014). Betting Against Beta. *Journal of Financial Economics*, 111(1), 1--25.

Moskowitz, T. J., & Grinblatt, M. (1999). Do Industries Explain Momentum? *Journal of Finance*, 54(4), 1249--1290.

```{r footer_en, results='asis'}
cat(sprintf('<div class="footer">
<div style="text-align: center; margin-bottom: 15px;">
<hr style="width: 50%%; border-color: #ddd;">
<em>End of Report</em><br>
<span>Quant Module Research Team | Confidential | %s</span>
</div>
<div class="disclaimer">
<strong>DISCLAIMER:</strong> This report is produced for internal research purposes only and does not constitute investment advice. Past performance does not guarantee future results. All backtested results are hypothetical and subject to model risk, data limitations, and implementation shortfall. The strategy has not been live-traded. Confidential --- do not distribute.
</div>
</div>', format(Sys.Date(), "%B %Y")))
```
